Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
methods: honing & typos (v3)

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio track of the
audio-description is the audio track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

% AV design matrix
For the subsequent first level GLM analysis, the modeled hemodynamic responses
related to all movie cuts (including \texttt{no\_cut}) and six low-level
perceptual confounds (s. Table \ref{tab:av-events}) were included as regressors
in the design matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included (s. Table \ref{tab:ao-events}).
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus [and to capture variance of a possibly confounding change of the
soundscape after a cut], we implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level general linear model (GLM) analyses to create
subject-specific results ($Z$-maps) across the 8 segments for every subject and
each stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of non-spatial information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts})
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).
% why
We assumed that category \texttt{vse\_new} on average comprised the most movie
frames depicting a landscape or the geometry of a setting, and the category
\texttt{vpe\_old} the most frames depicting persons, faces, or objects [(cf.
rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with not
just nouns referring to a person's head or face (\texttt{fahead}, N=83; e.g.
``eyes'', ``face'', or ``head'') but also all non-geometry related categories
(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}) except \texttt{furniture} to get more events
per stimulus segment.
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% c) the narrator is often lacking behind a short dialogue or a change of the
% soundscape that might already indicate a change of settings.
%
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
% (2010)
In the VIS study \citep{sengupta2016extension} using the established approach of
contrasting blocks of pictures, assessment of individual PPAs was based on
chosing post-hoc one from a set of three contrasts (\textit{strict},
\textit{relaxed}, and \textit{simple} contrast \citep{sengupta2016extension};
cf. Table 3 in \citep{sengupta2016extension}).

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the
    audio-visual movie (AV).
    Contrast 1-5 aim to isolate the PPA.
    Contrast 6-9 serve as negative control.
    Contrast 10 serves as control for moments when the narrator indicates the
    a switch of settings, events that could be correlated with a
    change of the soundscape.}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & vse\_new > vpe\_old & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
\end{tabular}
\end{table*}

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AD).
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Subject-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) via linear transformation to a subject-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}) and,
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

% second level model
The second level analyses which averaged contrast estimates over the eight
stimulus segments were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding (Z>2.3 in subject-space; Z>3.4 in group space)
(Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.

% third level model
The third level analysis which averaged contrast estimates over subjects was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
p=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
PPA region of interest (ROI) masks for individual subjects and a PPA group mask
of individual PPA overlaps were created from data provided by
\citep{sengupta2016extension}.

@@

% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

>>>>

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).

% we checked correlations
Since we annotated events in fixed time courses, the modeled hemodynamic
time-series could be correlated leading to shared variance and thus low
detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio track of the
audio-description is the audio track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

% AV design matrix
For the subsequent first level GLM analysis of the AV stimulus, the modeled
hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
six low-level perceptual confounds were included as regressors in the design
matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included.
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus, we also implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also included.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level general linear model (GLM) analyses to create
subject-specific results across the 8 segments for every subject and each
stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of non-spatial information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).
% why
We assumed that the category \texttt{vse\_new} on average comprised the most
movie frames depicting a landscape or the geometry of a setting, and the
category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
[(cf.  rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted buildings and
landmarks (\texttt{geo}), and rooms and geometry-defining objects
(\texttt{geo-room}) with not just nouns referring to a person's head or face
(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise nouns that could count as a member of another category
(e.g. ``[a] physician''; section \ref{rationale}), and
% richness of verbal description vs. picture
b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures].
% and c) the narrator is often lacking behind a short dialogue or a change of
% the soundscape that might already indicate a change of settings.

% control contrasts
Finally, we created several $t$-contrasts as negative controls for both stimuli
(see Tables \ref{tab:av-contrasts} and \ref{tab:ao-contrasts}).
% AV: no cut > cut
For the AV stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts.

% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
% (2010)
In the VIS study using the established approach of contrasting blocks of
pictures, a set of three contrasts (\textit{strict}, \textit{relaxed}, and
\textit{simple} was created contrast (cf. \citep{sengupta2016extension}).

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the
    audio-visual movie.
    Contrast 1-5 aim to isolate the PPA.
    Contrast 6-9 serve as negative control.
    Contrast 10 serves as control for moments when the narrator indicates
    a switch of settings.}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & vse\_new > vpe\_old & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
\end{tabular}
\end{table*}

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus.
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Subject-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) via linear transformation to a subject-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}), and
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

% second level model
The second level analyses which averaged contrast estimates over the eight
stimulus segments were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding (Z>2.3 in subject-space; Z>3.4 in group space)
(Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a cluster-corrected significance threshold of p=.05
\citep{worsley2001statistical}.

% third level model
The third level analysis which averaged contrast estimates over subjects was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
p=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
individual PPA overlaps were created from data provided by
\citep{sengupta2016extension}.

@@

% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (cf. Table 3 in \citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster (cf. Table 3 in  that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.
